Linear instability underlying synchronous waving of marine grass in flow

### 2014-08-30 Paper/grass.tex
Removed observed=predicted figure from text
combined graphs frequency

Considering small perturbations $u, v, p$ about the base profile $U$ and $P$ respectively, equation \eqref{navier-stokes} expanded to linear order in the perturbations yields
\begin{equation}
\begin{split}
\frac{\del u}{\del t}+U\frac{\del u}{\del x}+v\frac{\del U}{\del y} &= -\frac{1}{\rho}\frac{\del p}{\del x}+\frac{\mu}{\rho}\nabla^2u-2S(y) C_{N}dN_{g}Uu, \\
\frac{\del v}{\del  t}+ U\frac{\del v}{\del x} &= -\frac{1}{\rho}\frac{\del p}{\del y}+\frac{\mu}{\rho}\nabla^2v, \hspace{0.3cm} \nabla\cdot\bu=0.
 %\nabla\cdot \bu &= 0
\end{split}
\end{equation}
These equations can be non-dimensionalized using half channel height $H$, velocity $U_0$, and the associated advection time $H/U_0$ . 
We are left with three non-dimensional parameters in the model, viz. the Reynolds number $\Rey$, the vegetation drag parametrized by $C_N d H N_g = \Rey/\epsilon$, 
and the submergence ratio of the grass $h_g/H$. With these scaling, and using a stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance, we seek a wave solution of the form $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma t}$ to  obtain a modified Orr-Sommerfield equation. The eigenvalue $\sigma$ for a given $k$ provides growth rate and frequency associated with a perturbation of wavelength $2\pi/k$ through the solution of
% \small
\begin{equation}
\begin{split}
\left(D^2 -k^{2} \right)^2\phi &= \Rey \left[ \left({\sigma}+ikU\right) \left(D^2-k^2\right) -ikU_{yy}\right]\phi \\
&-D\left(2R \epsilon^{-1} S(y) U D \phi\right)
\label{Orr-somerfield}
\end{split}
\end{equation}
\shreyas{Boundary conditions?}
% \normalsize

\begin{figure}[htb]
\includegraphics[]{Critical_Re_vs_delta}
\caption{Critical Reynolds number with flow for different grass height as a function of inverse shear thickness}
\label{Re_vs_delta}
\end{figure}
A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. The dependence of this critical $\Rey$ on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the threshold\cite{Ghisal02} without any fitting parameters. The solution also predicts a finite critical wavenumber $k$ corresponding to this threshold for instability shown in Figure \ref{K_vs_shear}.

@@

\begin{figure}[htb]
\includegraphics[]{K_vs_shear_width_noshear}
\caption{Critical Wavenumber for different grass height as function of shear layer thickness}
\label{K_vs_shear}
\end{figure}
\begin{figure*}

%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens31_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens32_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens34_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens38_imgsc}}

\begin{tabular}{cccc}
{\includegraphics[scale = 0.72]{Set4_dens28_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens30_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens32_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens34_imgsc}} \\
{\includegraphics[scale = 0.72]{Set5_dens38_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens40_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens42_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens46_imgsc}} \\
{\includegraphics[scale = 0.72]{Set6_dens32_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens34_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens36_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens38_imgsc}}
\end{tabular}

@@

The regime of shear instability of flow above the 
grass further predicts that for large drag $\Rey \sim (\frac{\delta}{H})^{-3/2}$, which can be understood by asymptotic analysis of \eqref{Orr-somerfield}.
Noting that for large drag, non-dimensional flow velocity $U \sim (\frac{\delta}{H})^{3/2}$ inside the grass and $\Rey \gg 1$. So equation \eqref{Orr-somerfield}
can be simplified considerably both with in the grass and above the grass canopy. As $U_{yy}\sim 0$ inside the grass and $\frac{1}\Rey \ll 1$,
the equation within the grass simplifies into
$\sigma\left(\phi_{yy}-k^2\phi\right) = -\frac{\del}{\del y}\left(\frac{2\phi_y}{\delta^{3/2}\Rey}\right)$ while in the unvegetated region it simplifies into Rayleigh equation 
$ \left(\sigma+ikU\right) \left(D^2-k^2\right)\phi =  ikU_{yy}\phi$. From the balance of coefficients of $\phi_{yy}$ inside the grass we can easily estimate that asymptotically 
$\Rey \sim (\frac{\delta}{H})^{-3/2}$.
\begin{figure}[]
\includegraphics[]{Asymptotic_eig_set3.pdf}
\caption{plot of $|\phi|$ for different shear layer thickness in limit of small shear layer thickness}
\label{Asymptotic_mode}
\end{figure}
\begin{figure}[htb]
\includegraphics[scale=0.34]{Observed_vs_calculated}
\caption{Comparison between experimently oberved frequency and predicted frequency}
\label{Observed_calculated}
\end{figure}

>>>>

Considering small perturbations $u, v, p$ about the base profile $U$ and $P$ respectively, equation \eqref{navier-stokes} expanded to linear order in the perturbations yields
\begin{equation}
\begin{split}
\frac{\del u}{\del t}+U\frac{\del u}{\del x}+v\frac{\del U}{\del y} &= -\frac{1}{\rho}\frac{\del p}{\del x}+\frac{\mu}{\rho}\nabla^2u-2S(y) C_{N}dN_{g}Uu, \\
\frac{\del v}{\del  t}+ U\frac{\del v}{\del x} &= -\frac{1}{\rho}\frac{\del p}{\del y}+\frac{\mu}{\rho}\nabla^2v, \hspace{0.3cm} \nabla\cdot\bu=0.
 %\nabla\cdot \bu &= 0
\end{split}
\end{equation}
These equations can be non-dimensionalized using half channel height $H$, velocity $U_0$, and the associated advection time $H/U_0$ . 
We are left with three non-dimensional parameters in the model, viz. the Reynolds number $\Rey$, the vegetation drag parametrized by $C_N d H N_g = \Rey/\epsilon$, 
and the submergence ratio of the grass $h_g/H$. With these scaling, and using a stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance, we seek a wave solution of the form $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma t}$ to  obtain a modified Orr-Sommerfield equation. The eigenvalue $\sigma$ for a given $k$ provides growth rate and frequency associated with a perturbation of wavelength $2\pi/k$ through the solution of
% \small
\begin{equation}
\begin{split}
\left(D^2 -k^{2} \right)^2\phi &= \Rey \left[ \left({\sigma}+ikU\right) \left(D^2-k^2\right) -ikU_{yy}\right]\phi \\
&-D\left(2R \epsilon^{-1} S(y) U D \phi\right)
\label{Orr-somerfield}
\end{split}
\end{equation}
\shreyas{Boundary conditions?}
% \normalsize
\begin{figure}
\begin{tabular}{c}
%\begin{figure}[htb]
{\centering{\includegraphics[]{Critical_Re_vs_delta_noshear}}}\\
{\centering{\includegraphics[]{K_vs_shear_width_noshear}}}\\
%\caption{Critical Reynolds number with flow for different grass height as a function of inverse shear thickness}
%\label{Re_vs_delta}
%\end{figure}
\end{tabular}
\end{figure}
A threshold in $\Rey$ for the onset of the instability naturally emerges from the solution of \eqref{Orr-somerfield}. The dependence of this critical $\Rey$ on the $\delta/H$ and $\hg/H$ is shown in figure \ref{Re_vs_delta}, and compared with experimental observation of the threshold\cite{Ghisal02} without any fitting parameters. The solution also predicts a finite critical wavenumber $k$ corresponding to this threshold for instability shown in Figure \ref{K_vs_shear}.

@@

%\begin{figure}[htb]
%\includegraphics[]{K_vs_shear_width_noshear}
%\caption{Critical Wavenumber for different grass height as function of shear layer thickness}
%\label{K_vs_shear}
%\end{figure}

\begin{figure*}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens31_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens32_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens34_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens38_imgsc}}
\begin{tabular}{cccc}
{\includegraphics[scale = 0.72]{Set4_dens28_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens30_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens32_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens34_imgsc}} \\
{\includegraphics[scale = 0.72]{Set5_dens38_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens40_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens42_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens46_imgsc}} \\
{\includegraphics[scale = 0.72]{Set6_dens32_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens34_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens36_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens38_imgsc}}
\end{tabular}

@@

The regime of shear instability of flow above the 
grass further predicts that for large drag $\Rey \sim (\frac{\delta}{H})^{-3/2}$, which can be understood by asymptotic analysis of \eqref{Orr-somerfield}.
Noting that for large drag, non-dimensional flow velocity $U \sim (\frac{\delta}{H})^{3/2}$ inside the grass and $\Rey \gg 1$. So equation \eqref{Orr-somerfield}
can be simplified considerably both with in the grass and above the grass canopy. As $U_{yy}\sim 0$ inside the grass and $\frac{1}\Rey \ll 1$,
the equation within the grass simplifies into
$\sigma\left(\phi_{yy}-k^2\phi\right) = -\frac{\del}{\del y}\left(\frac{2\phi_y}{\delta^{3/2}\Rey}\right)$ while in the unvegetated region it simplifies into Rayleigh equation 
$ \left(\sigma+ikU\right) \left(D^2-k^2\right)\phi =  ikU_{yy}\phi$. From the balance of coefficients of $\phi_{yy}$ inside the grass we can easily estimate that asymptotically 
$\Rey \sim (\frac{\delta}{H})^{-3/2}$.
\begin{figure}[]
\includegraphics[]{Asymptotic_eig_set3.pdf}
\caption{plot of $|\phi|$ for different shear layer thickness in limit of small shear layer thickness}
\label{Asymptotic_mode}
\end{figure}
%\begin{figure}[htb]
%\includegraphics[scale=0.34]{Observed_vs_calculated}
%\caption{Comparison between experimently oberved frequency and predicted frequency}
%\label{Observed_calculated}
%\end{figure}
